---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::markdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("AshenWELI/Assignment4")
library(assignment4)
```

### import sample dataset iris
```{r}
data(iris)
```

### create a linreg mode object using linreg@new function
```{r}
linreg_mod_object <- linreg$new(Petal.Length~Species, data = iris)
```

### print the coefficients and coefficient names according to multiple regression model
```{r}
linreg_mod_object$print()
```

### print two plots: Residuals vs Fitted and Scale−Location 
```{r}
linreg_mod_object$plot()
```

### print residuals e^ 
```{r}
linreg_mod_object$resid()
```

### print predicted values y^
```{r}
linreg_mod_object$pred()
```

### print the coefficients
```{r}
linreg_mod_object$coef()
```

### print summary statistics
including the coefficients with their standard error, t-value and p-value as well as the estimate of ^ σ and the degrees of freedom in the model
```{r}
linreg_mod_object$summary()
```
